\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{titlesec}
\usepackage{needspace}


\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}
  [\needspace{5\baselineskip}]

   
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.75]{geometry}
\usepackage[english]{babel}
\usepackage{setspace}
\nopagenumbers{}   
\onehalfspacing
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

\name{Martin}{Hablák}
\title{Curriculum Vitae}
\born{22 September 1981}                                 % optional, remove / comment the line if not wanted
\address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+421~(905)~121~126}
\email{martin.hablak@gmail.com}    
\address{Jána Stanislava 47}{Bratislava 84105}{Slovakia}
\social[github]{xmatoha}   

\begin{document}

\makecvtitle

\section{Education}
\cventry{2005--2007}{Msc}{Slovak Technical University}{Bratislava} {\textit{Faculty of Electrical Engineering and Informatics}}{}  % arguments 3 to 6 can be left empty
\cventry{2000--2005}{Bsc}{Slovak Technical University}{Bratislava} {\textit{Faculty of Informatics and Information Technology}}{}  % arguments 3 to 6 can be left empty


\section{Experience}
\cventry{2020--present}{Cloud Pak For Data Platform Architect}{IBM}{Bratislava}{}{Building Cloud Pak For Data Platform for internal IBM users.
\begin{itemize}%
\item I designed platform architecture
\item Developed disaster recovery procedures, monitoring and healtcheck to improve availablity
\item Automated installation, upgrading and configuration process
\item Developed boarding process using ServiceNow using Python
\end{itemize}}

\cventry{2020--present}{MLOps Engineer}{IBM}{Bratislava}{}{Supporting Data scientist with various software related tasks. 
\begin{itemize}%
\item Developed services to integrate with Cloud Pak For Data (Python)
\item Contributed to library helping Data Scientist and Data Engineers bootstrapping their projects (Python)
\end{itemize}}

\cventry{2018--2020}{Software Engineer}{IBM}{Bratislava}{}{Helping teams to adopt Extreme programming practices. Developing DevOps platform for our internal software teams. 
\begin{itemize}%
\item Delivered DevOps platform on JenkinX
\item Created custom automation using Golang  
\item Leading Extreme programming training
\end{itemize}}

\cventry{2017--2018}{Software Engineer}{IBM}{Bratislava}{}{I was responsible for development of internal IBM news service {}%
\begin{itemize}%
\item Implemented backend services for IBM news service in NodeJS using Cassandra and Solr as datastores
\end{itemize}}
  

\cventry{2014--2018}{Lead Software Engineer}{IBM}{Bratislava}{}{I was responsible for development of IBM internal employee directory service. \newline{}%
Solution served whole IBM population. It consisted of multiple microservices written in Java (Websphere Librety Profile, Vertx). It had advanced ``google like'' search capabilities. It integrated with various internal systems using batch processing, real time processing. 
\begin{itemize}%
\item Designed and implemented services which were used by almost any application in IBM
\item Developed CI/CD process using Ansible  
\item Services used various datastores. CouchDb for holding employee data. Solr as search engine. Redis as pass through cache.
\item Services were implemented using Websphere Librety.
\item Performance critical services were implemented in VertX.  
\end{itemize}}

\cventry{2012--2014}{Software Developer}{IBM}{Bratislava}{}{DataStage/Java Developer in Finance. Data preparation for machine learning algorithms predicting IBM outer close revenue.
\begin{itemize}%
\item Develop DataStage extension to integrate with IBM TM1 OLAP Cube
\item Develop DataStage jobs to prepare data for machine learning algorithms
\end{itemize}}

\cventry{2010--2012}{Software Developer}{SwissRe}{Bratislava}{}{Java Developer in Finance, working on new system for Fiance Reporting. Software was build on Websphere application server running of IBM System Z.
\begin{itemize}%
\item Rewriting Cobol modules to Java
\item Was part of developing modern data processing platform
\end{itemize}}

\cventry{2007--2010}{Software Developer}{IBM}{Bratislava}{}{ETL developer Java Lotus Notes
\begin{itemize}%
\item Develop ETL library to transfer data from Lotus Notes to DB2
\item Manage system of nightly data loads of Sales Opportunities
\end{itemize}}


\section{Skills}
\cvskilllegend*[1em]{}
\setcvskillcolumns[][0.45][\widthof{``Year''}]%
\setcvskillcolumns[][][\widthof{``Year''}]%
\setcvskilllegendcolumns[][0.6]%
\cvskillhead[-0.1em]
\cvskillentry*{Language:}{4}{Python}{3}{Implemented MLOps Tooling Using Python, Rest services using FastAPI}
\cvskillentry*{Language:}{3}{Golang}{1}{Implemented Kubernetes automation using Golang}
\cvskillentry*{Language:}{4}{NodeJs}{4}{Implemented multiple NodeJs services in ExpressJs and Fastify}
\cvskillentry*{Language:}{2}{Clojure}{1}{Used Clojure for Extreme Programming Training}
\cvskillentry*{Language:}{4}{Java}{7}{Used Java/Websphere/Spring/Vert.X implementing REST services for various projects}

\cvskillentry*{Platform:}{3}{Kubernetes/Docker}{3}{Configured maintained and supported Openshift Clusters with Cloud Pak For Data platform}

\cvskillentry*{MLOps:}{2}{DVC}{1}{Implemented solution integrating DVC with Watson Machine learning service}

\cvskillentry*{MLOps}{3}{MLFlow}{3}{Experimenting with MLFlow for experiment tracking and model registry for our Data Scientists}

\cvskillentry*{MLOps:}{3}{Cloud Pak For Data}{3}{Configured, maintained  Openshift Clusters with Cloud Pak For Data platform}



\cvskillentry*{Database:}{4}{Couchdb}{4}{Created directory service service using CouchDb as main data store}
\cvskillentry*{Database:}{3}{Cassandra}{1}{Created IBM internal news page using Cassandra}
\cvskillentry*{Database:}{2}{Redis}{2}{Used Redis as cache for directory service}
\cvskillentry*{Database:}{3}{Solr/Elastic Search}{4}{Used Solr as search engine for directory service}
\cvskillentry*{Database:}{3}{Postgresql/Db2 - Relational Databases}{10}{Used relational database on various project as main data store}

\cvskillentry*{Programming Technique:}{3}{Extreme Programming}{3}{Worked as Extreme Programming coach. Practicing Test Drive Development, Behavior Drive Development, DevSecOps techniques}
\cvskillentry*{Soft skill:}{1}{Coaching}{1}{Attended business coaching education. Practicing coaching technique at work.}


\section{Interests}
\cvitem{Outdoor sports}{Cycling, Ski mountaineering, Climbing, ...}
\cvitem{Reading}{lately SciFi}
\cvitem{Microbit}{Exploring microbit with my kids}


\end{document}
